### 2021-07-14 src/paper/results/rapid_tests_statistics.tex
Fix broken references.
More polishing.

In order to make most use out of limited data sources on rapid test usage, we model the
number of performed rapid tests as a result of time invariant willingness to do rapid
tests and time varying supply side factors and events that trigger rapid tests. Thus, the
$\pi$ parameters governing when individuals do rapid tests described in
Section~\ref{subsec:rapid_test_demand} are only indirectly related to the number of rapid
tests that are actually performed in the model. When it comes to positive and negative
rapid tests, there is even an additional layer because rapid tests are imperfectly
sensitive and specific.

@@

We start with the share of the population doing a rapid test, receiving a positive rapid
test and receiving a negative rapid test over time by the channel through which the test
was demanded in Figures~\ref{fig:rapid_test_demand_by_channel},
\ref{fig:pos_rapid_tests_by_channel} and \ref{fig:neg_rapid_tests_by_channel},
respectively. Overall, the share of the population getting a rapid test on a given day
increases from 2\% in mid March to over 10\% by May. The work rapid tests are a little
ragged because of public holidays. For education rapid tests both vacations (first half
of April) as well as the opening of schools in May are very visible in the rapid test
demand. Overall, work tests make up the largest fraction of rapid tests. The image is
very similar for the share of positive tests, except that the overall number of positive
tests starts decreasing in May as rapid test expansion comes to a halt and cases fall,
especially the positive share of private rapid tests falls as less and less individuals
are triggered to seek a rapid test because of a risk contact in their household.

@@

Next, we show the tests split by whether they are true positive, false positive, true
negative or false negative (see Figure~\ref{fig:rapid_test_results_numbers}) in numbers
per million individuals to make the metric comparable to incidences.
% true positive
The number of true positives (Figure~\ref{fig:rapid_tests_number_true_positive}) rapidly
increases and peaks at the end of April with over 200 cases per million detected through
rapid tests per day. This means that our model suggests that Germany was able to detect
up to 16,600 cases per day that would have likely gone undetected otherwise. The most
powerful tool for detecting cases are the private rapid tests. This is because a large
share of them are targeted, i.e. triggered by events in the household. However, this
does not mean that rapid tests in the workplace or at school are useless. It is rather
the combination of large scale screening at work and in schools and very efficient
follow up tests whenever those screening tests detected a case. Shapley values
(Figure~\ref{fig:2021_scenarios_decomposition_tests}) take this into account and
assign about 50\% of the overall reduction of case numbers via rapid tests to private
rapid tests with work and school rapid tests accounting for 40\% and 7\%,
respectively.

@@

This shows clearly that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are positive. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.

\begin{figure}   % Number of True Positive / False Positive / True Negative / False Negative
    \centering
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_true_positive}
        \caption{Number of Discovered Cases Due to Rapid Tests by Channel}
        \label{fig:rapid_tests_number_true_positive}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_false_positive}
        \caption{Number of False Positive Rapid Tests by Channel}
        \label{fig:rapid_tests_number_false_positive}
    \end{subfigure}
    \vskip3ex
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_true_negative}
        \caption{Number of True Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_number_true_negative}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_false_negative}
        \caption{Number of False Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_number_false_negative}
    \end{subfigure}
    \vskip3ex
    \caption{Rapid Test Results}
    \label{fig:rapid_test_results_numbers}
    \floatfoot{\noindent \textit{Note:}
        Each panel shows the number of rapid tests per million inhabitants that fall into the
        respective category. Private rapid tests are especially good at detecting cases but
        since they are often triggered by rapid tests from other channels, the other groups
        of tests, especially rapid tests at the workplace, also play an important role for
        containing the pandemic.}
\end{figure}

@@

A similar picture arises, when looking at the false positive rate,
i.e. the share of positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shows that the false
positive rate is very high. On average 60\% to 93\% of positive tests are
received by individuals that are not infected. The false positive rate increases over
time. This is due to the low prevalence of infections in the population, which falls
over time. Again, private rapid tests are an exception with a much lower false
positive rate because those tests are primarily demanded when there is a high likelihood
of being infected. The low false negative rate of 0.2\% looks very low. As discussed
above this is deceiving and just a mechanical consequence of a very low prevalence
of the disease and the many rapid tests done by non-infected people.

\begin{figure} % True Positive / False Positive / True Negative / False Negative Rate
    \centering
    % \begin{subfigure}[b]{0.425\textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/true_positive_rate}
    %     \caption{Rate of True Positive Rapid Tests by Channel}
    %     \label{fig:rapid_tests_true_positive_rate}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/false_positive_rate}
        \caption{Rate of False Positive Rapid Tests by Channel}
        \label{fig:rapid_tests_false_positive_rate}
    \end{subfigure}
    % \vskip3ex
    % \begin{subfigure}[b]{0.425\textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/true_negative_rate}
    %     \caption{Rate of True Negative Rapid Tests by Channel}
    %     \label{fig:rapid_tests_true_negative_rate}
    % \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/false_negative_rate}
        \caption{Rate of False Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_false_negative_rate}
    \end{subfigure}
    \vskip3ex
    \caption{Rapid Test Rates by Channel}
    \label{fig:rapid_test_results_rates}

    \floatfoot{\noindent \textit{Note:}
        The left panel shows the share of positive tests that are given to people who are not
        infected. This share is large as can be expected with a very low baseline rate of
        positive individuals. As the incidence in the population drops, the false positive
        rate increases. An exception are the private rapid tests because they are --
        especially when the incidence is high -- often triggered by events that make it
        likely that the test taker is infected and therefore their false positive rate is
        much lower. The right panel shows the false negative rate in the population, i.e. the
        share of negative test results that are mistakenly given to infected individuals.
        This is very low because there are many truly negative tests in times of low
        incidences and large scale screening tests.}
\end{figure}

>>>>

In order to make the most use out of limited data sources on rapid test usage, we model the
number of performed rapid tests as a result of time invariant willingness to do rapid
tests and time varying supply side factors and events that trigger rapid tests. Thus, the
$\pi$ parameters governing when individuals do rapid tests described in
Section~\ref{subsec:rapid_test_demand} are only indirectly related to the number of rapid
tests that are actually performed in the model. When it comes to positive and negative
rapid tests, there is even an additional layer because rapid tests are imperfectly
sensitive and specific.

@@

We start with the share of the population doing a rapid test and receiving a positive rapid
test over time by the channel through which the test
was demanded in Figures~\ref{fig:rapid_test_demand_by_channel},
\ref{fig:pos_rapid_tests_by_channel}, respectively. Overall, the share of the population
getting a rapid test on a given day increases from 2\% in mid March to over 10\% by May.
The work rapid tests are a little ragged because of public holidays. For education rapid
tests both vacations (first half of April) as well as the opening of schools in May are
very visible in the rapid test demand. Overall, work tests make up the largest fraction
of rapid tests. The image is very similar for the share of positive tests, except that
the overall number of positive tests starts decreasing in May as rapid test expansion
comes to a halt and cases fall, especially the positive share of private rapid tests
falls as less and less individuals are triggered to seek a rapid test because of a risk
contact in their household.

@@

Next, we show the tests split by whether they are true positive, false positive, true
negative or false negative (see Figure~\ref{fig:rapid_test_results_numbers}) in numbers
per million individuals to make the metric comparable to incidences.

The number of true positives (Figure~\ref{fig:rapid_tests_number_true_positive}) rapidly
increases and peaks at the end of April with over 200 cases per million detected through
rapid tests per day. This means that our model suggests that Germany was able to detect
up to 16,600 cases per day that would have likely gone undetected otherwise. The most
powerful tool for detecting cases are the private rapid tests. This is because a large
share of them are targeted, i.e. triggered by events in the household. However, this
does not mean that rapid tests in the workplace or at school are less important. It is rather
the combination of large scale screening at work and in schools and very efficient
follow up tests whenever those screening tests detected a case. Shapley values
(Figure~\ref{fig:2021_scenarios_decomposition_tests}) take this into account and
assign about 50\% of the overall reduction of case numbers via rapid tests to private
rapid tests with work and school rapid tests accounting for 40\% and 7\%,
respectively.

@@

This shows clearly that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are infected. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.

\begin{figure}   % Number of True Positive / False Positive / True Negative / False Negative
    \centering
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_true_positive}
        \caption{Number of Discovered Cases Due to Rapid Tests by Channel}
        \label{fig:rapid_tests_number_true_positive}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_false_positive}
        \caption{Number of False Positive Rapid Tests by Channel}
        \label{fig:rapid_tests_number_false_positive}
    \end{subfigure}
    \vskip3ex
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_true_negative}
        \caption{Number of True Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_number_true_negative}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/number_false_negative}
        \caption{Number of False Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_number_false_negative}
    \end{subfigure}
    \vskip3ex
    \caption{Simulated Rapid Test Statistics}
    \label{fig:rapid_test_results_numbers}
    \floatfoot{\noindent \textit{Note:}
        Each panel shows the number of rapid tests per million inhabitants that fall into the
        respective category. Private rapid tests are especially good at detecting cases but
        since they are often triggered by rapid tests from other channels, the other groups
        of tests, especially rapid tests at the workplace, also play an important role for
        containing the pandemic. All results are averaged over 30 simulation runs.
        For legibility reasons, all lines are rolling 7-day averages.
        }
\end{figure}

@@

A similar picture arises, when looking at the false positive rate,
i.e. the share of positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shows that the false
positive rate is very high. On average 60\% to 93\% of positive tests are
received by individuals that are not infected. The false positive rate increases over
time. This is due to the low prevalence of infections in the population, which falls
over time. Again, private rapid tests are an exception with a much lower false
positive rate because those tests are primarily demanded when there is a high likelihood
of being infected. The false negative rate of 0.2\% looks very low. As discussed
above this is deceiving and just a mechanical consequence of a very low prevalence
of the disease and the many rapid tests done by non-infected people.

\begin{figure} % True Positive / False Positive / True Negative / False Negative Rate
    \centering
    % \begin{subfigure}[b]{0.425\textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/true_positive_rate}
    %     \caption{Rate of True Positive Rapid Tests by Channel}
    %     \label{fig:rapid_tests_true_positive_rate}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/false_positive_rate}
        \caption{Rate of False Positive Rapid Tests by Channel}
        \label{fig:rapid_tests_false_positive_rate}
    \end{subfigure}
    % \vskip3ex
    % \begin{subfigure}[b]{0.425\textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/true_negative_rate}
    %     \caption{Rate of True Negative Rapid Tests by Channel}
    %     \label{fig:rapid_tests_true_negative_rate}
    % \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/false_negative_rate}
        \caption{Rate of False Negative Rapid Tests by Channel}
        \label{fig:rapid_tests_false_negative_rate}
    \end{subfigure}
    \vskip3ex
    \caption{False Positive and False Negative Rates by Channel}
    \label{fig:rapid_test_results_rates}

    \floatfoot{\noindent \textit{Note:}
        The left panel shows the share of positive tests that are given to people who are not
        infected. This share is large as can be expected with a very low baseline rate of
        positive individuals. As the incidence in the population drops, the false positive
        rate increases. An exception are the private rapid tests because they are --
        especially when the incidence is high -- often triggered by events that make it
        likely that the test taker is infected and therefore their false positive rate is
        much lower. The right panel shows the false negative rate in the population, i.e. the
        share of negative tests done by infected individuals.
        This is very low because there are many truly negative tests in times of low
        incidences and large scale screening tests.}
\end{figure}

### 2021-07-14 src/paper/results/share_known_cases.tex
More polishing.

We show the age group specific share of detected cases in
Figure~\ref{fig:share_known_cases_by_age_group}.\footnote{We explain how we model the
detection of cases in Section~\ref{sub:testing} and show the overall share of detected
cases that we use as input for our testing model in
Section~\ref{subsec:data_share_known_cases}.}

In 2020 the share of detected cases is much higher in older age groups as they are much
more likely to develop symptoms and symptomatic individuals are much more likely to be
tested. Starting in 2021 the share of detected cases not only depends on the overall
share of detected cases we feed into our model but also on the number of performed rapid
tests. As more and more (often asymptomatic and presymptomatic) individuals receive
positive rapid tests and receive confirmation, the share of detected cases starts to
increase, especially after March when rapid tests became much more widely available. This
effect is very visible for school pupils, (5-14, green line). As twice weekly rapid tests
become mandatory in schools and students start going to school after the Easter break,
the share of detected cases for that group increases drastically from 25\% to over 60\%
between April and June.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation for each age group in our population.
  We use the overall share of detected cases that was estimated through the case fatality
  ratio by \citet{Dunkelzifferradar2020} for all of 2020 and then assume it to be
  constant as vaccinations of the elderly strongly affect the case fatality rate which
  the project does not account for. To get from an overall share of detected cases to the
  share of cases that is detected in each age group we use that asymptomatic cases are
  much less likely to be detected. As our model covers age specific asymptomatic rates
  this endogenously leads to group specific share of detected cases that suggest that
  infections in younger age groups are under-detected. Starting in 2021 in addition to
  the overall numbers of detected cases through symptoms and the share of detected cases,
  cases are also detected through confirmation of positive rapid tests. This leads to an
  increase in the share of detected cases for all age groups but in particular for the
  younger age groups that are covered extensively with rapid tests through the rapid test
  requirement for participating in school. Age groups that have a high share of workers
  also disproportionately increase their detection rate.}
\end{figure}

>>>>

This section shows the share of detected cases for different age groups. See
Section~\ref{sub:testing} for an explanation of how we model the detection of cases
and Section~\ref{subsec:data_share_known_cases} for the calibration of the relevant
parameters.

The share of detected cases fall drastically from October to December when the
incidence of CoViD-19 skyrocketed, PCR tests were still scarce and official contact
tracing became impossible due to the sheer amount of cases.

As rapid tests become available and more and more individuals receive positive rapid
tests and seek PCR tests, the share of detected cases starts to increase. While first
rapid tests are available since the beginning of 2021 the effect only becomes substantial
after March when access to rapid tests was greatly expanded.

Overall, the share of detected cases is much higher in older age groups. This is because
the likelihood to develop symptoms increases with age and symptomatic cases are
more likely to be detected.

A notable exception is that school age children (5-14, green line) overtake the next age
group in May 2021. This comes from a particularly strong increase in their share of
detected cases after Easter, when weekly rapid tests become mandatory in schools.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case for each age group in our simulated population.
  For legibility reasons, all lines are rolling 7-day averages.}
\end{figure}

### 2021-07-14 src/paper/results/validation.tex
More polishing.

Achieving a good in-sample fit does not necessarily guarantee that our model will also be
able to make out of sample predictions. For example, it could be that the results are
very sensitive to the exact number of vaccinations, the work mobility multiplier
($\rho_{w,\:attend,\:t}$) or the number of rapid tests (governed by the $\pi$ parameters)
that are performed -- all of which are things that cannot be exactly known ex-ante.

@@

  \floatfoot{\noindent \textit{Note:} Number of rapid tests performed in the different
  prediction scenarios. All scenarios are the same until March 1 and have the same level
  of rapid tests when all supply constraints are resolved. They differ in the date at
  which the full number of tests is reached. For students ($\pi_{students,\:t}$) and
  teachers ($\pi_{teacher,\:t}$) the full number of rapid tests is reached after the
  Easter holidays in all scenarios. For rapid tests in the workplace ($\pi_{w,\:s,\:t}$)
  and private rapid tests ($\pi_{private,\:t}$) it is reached between May 1 and June 10,
  depending on the scenario. }
\end{figure}

@@

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the Easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations.}
\end{figure}

>>>>

Achieving a good in-sample fit does not necessarily guarantee that our model will also be
able to make out of sample predictions. For example, it could be that the results are
very sensitive to the exact number of vaccinations, the work mobility multiplier
($\rho_{w,\:attend,\:t}$) or the number of rapid tests (governed by the $\pi$ parameters)
that are performed -- all of which are things that cannot be known exactly ex-ante.

@@

  \floatfoot{\noindent \textit{Note:} Number of rapid tests performed in the different
  prediction scenarios. All scenarios are the same until March 1 and have the same level
  of rapid tests when all supply constraints are resolved. They differ in the date at
  which the full number of tests is reached. For students ($\pi_{students,\:t}$) and
  teachers ($\pi_{teacher,\:t}$) the full number of rapid tests is reached after the
  Easter holidays in all scenarios. For rapid tests in the workplace ($\pi_{w,\:s,\:t}$)
  and private rapid tests ($\pi_{private,\:t}$) it is reached between May 1 and June 10,
  depending on the scenario.}
\end{figure}

@@

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the Easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations. For legibility reasons, all lines are rolling 7-day averages.}
\end{figure}
